%-------------------------
% Resume in Latex
% Author: Shreyan Sardar
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{10pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% --- FIXED: Removed leading non-breaking space before \vspace ---
\titleformat{\section}{
\vspace{-6pt}\raggedright\Large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
% --- FIXED: Removed leading non-breaking spaces ---
\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small #2} \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
% --- FIXED: Removed leading non-breaking spaces ---
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, label=$\bullet$]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
% --- UPDATED: Added LinkedIn and GitHub, organized into two lines for clarity ---
\begin{center}
    {\Huge \scshape Shreyan Sardar} \\ \vspace{10pt}
    \small \faPhone\ +91 9123669842 ~$\cdot$~ \href{mailto:shreyansardar427@gmail.com}{\faEnvelope\ shreyansardar427@gmail.com} \\ \vspace{4pt}
    \href{https://shreyandev.vercel.app/}{\faLaptop\ shreyandev.vercel.app} ~$\cdot$~
    \href{https://www.linkedin.com/in/shreyansardar/}{\faLinkedin\ linkedin.com/in/shreyansardar} ~$\cdot$~
    \href{https://github.com/ShreyanDev5}{\faGithub\ github.com/ShreyanDev5}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Recent Computer Science graduate focused on Java backend development with Spring Boot and Hibernate. Built full-stack applications using RESTful APIs and relational databases. Strong foundation in data structures and algorithms, ranked in the top 7\% globally on LeetCode.

%-----------SKILLS-----------
\section{Skills}
\textbf{Languages \& Frameworks:} Java, Spring Boot, Hibernate \\
\textbf{Databases:} SQL, MySQL, H2 \\
\textbf{Tools \& Technologies:} Docker, Redis, Maven, Git, REST APIs, JUnit 5, Postman, Lombok, IntelliJ IDEA \\
\textbf{Conceptual Knowledge:} System Design, Swagger / OpenAPI, Testcontainers, RabbitMQ / Kafka, CI/CD Pipelines, Kubernetes, AWS / Terraform, Observability \& Monitoring

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{SpringMart E-Commerce Platform} $|$ \emph{Java, Spring Boot, React, H2}}{2025}
    \resumeItemListStart
        \resumeItem{Built RESTful APIs with Spring Boot for CRUD operations on products and images.}
        \resumeItem{\sloppy Used Spring Data JPA with H2 for data persistence, handling product records and binary image storage.}
        \resumeItem{\sloppy Developed a responsive React frontend with AI-assisted tools, creating a complete full-stack application.}
    \resumeItemListEnd
\resumeProjectHeading
    {\textbf{Student Management System} $|$ \emph{Java, MySQL, JDBC, Maven}}{2025}
    \resumeItemListStart
        \resumeItem{\sloppy Built a Java console application using JDBC for student record management with CRUD operations and input validation.}
        \resumeItem{Created a reporting module with SQL queries to generate analytics on grade distribution and top-performer rankings.}
        \resumeItem{\sloppy Migrated from file-based storage to a MySQL database, improving data persistence and query efficiency.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
% --- FIXED (1 of 3): Escaped the '&' character.
% --- FIXED (3 of 3): Combined all 4 arguments into one command call.
\resumeSubheading
    {B.Tech in Computer Science \& Engineering}{2021 – 2025}
    {Pailan College of Management \& Technology (MAKAUT), Kolkata, India}{CGPA: 8.3 / 10}
\item \vspace{2pt}
    \resumeItemListStart
        \resumeItem{{\sloppy\textbf{Relevant Coursework:} Object-Oriented Programming, Database Management Systems (DBMS), Data Structures and Algorithms, Operating Systems, Computer Networks\par}}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\vspace{0pt}
\resumeItemListStart
% --- FIXED: Removed leading non-breaking spaces ---
\resumeItem{Earned the \textbf{LeetCode 50 Days Badge (2024)} --- Ranked in the \textbf{top 6.9\% globally} for consistent daily problem-solving}
\resumeItem{Solved \textbf{130+ Data Structures \& Algorithms problems} on LeetCode, covering \textbf{Dynamic Programming, Trie, DFS, BFS, Arrays, and Sorting}}
\resumeItemListEnd

\end{document}
